An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
add an algorithm

Each rule can be viewed as a mapping from 
lines $j$ and $k$ in a configuration file to a relation, $R$.

\[
\{ Rule = (a_j, a_k) | j \neq k \} \rightarrow \{ R \}
\]

Specifically, $a_j$ and $a_k$ are two different lines from our
intermediate representation, or more formally, $j \neq k \land
a_j, a_k \in \{ L \}$ where is the set of lines (key-value pairs) found
in the learning set. The relation $R$
is a Boolean function specific to the error to detect. 
As an example, to detect the error that key $k_1$ must always 
have a value greater than key $k_2$, the relation $R$ is $>$.

\para{Our approach.}
In \app's leaner module, the rule learning mechanism is tolerant 
enough to accept a dataset {\em full of} incorrect configuration files.
Rather than manually correcting each file, 
we extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).

>>>>

Each rule can be viewed as a mapping from 
attributes $a_j$ and $a_k$ in the intermediate representation of a 
configuration file to a boolean function, $R$: this can be represented by a rule
$r := (a_j, a_k) \rightarrow B_{rel}$.
$B_{rel}$ is a Boolean function specific to the relation to assess, meaning that 
the desired relation can either be satisfied or not satisfied. 
For instance, for the rule that {\tt max\_connections} must 
be greater than {\tt mysql.max\_persistent}, the relation of interest is $>$ 
and $B_{>}$ would be set to true.

\para{Our approach.}
In \app's learner module, the rule learning mechanism is tolerant 
enough to accept a dataset {\em full of} incorrect configuration files.
Rather than manually correcting each file, 
we extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).

\begin{algorithm}
\STATE Let $\theta$ be the list of possible types for the intermediate representation of interest.
\caption{Probabilistically Learn Rules}
  \begin{algorithmic}[1]
    \STATE learnRules($C$):\\
    Input: $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\
%    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
    \FOR{each file $F$ in $C$}
        \FOR{each entry $e$ in $F$}
               \IF{$g(e)$ is false}
                        \STATE continue to next entry
               \ENDIF
                \FOR{$\tau \in typelist(e)$}
                        \FOR{$t \in templates(\tau)$}
                        \IF{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
                                        \STATE update $p_{\tau}$ appropriately
%                                \ELSIF{anti($t$) is satisfied over rest of entries}
%                                        \STATE update $p_{\tau}$ appropriately
                                \ENDIF
                        %Check if $t$ is satisfied  over rest 
                        \ENDFOR
               \ENDFOR
          \ENDFOR
      \ENDFOR
  \end{algorithmic}
\end{algorithm}

%each entry is listed as (g,k,v,typelist)

### 2016-05-10 OSDI/trans.tex
add an algorithm

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. \app also allows users to 
provide extra help to the translator
for their specific system configurations,
but not necessarily. 
Each of the entries in the intermediate representations
have been assigned types, and these types would guide the learning
modules later.

\ennan{We need a kind of formal definition (using a figure) to
define the grammar of our intermediate representation. The basic
view of this definition should be similar to define a type language
grammar.}

\para{Introducing probabilistic types.}
For any key-value entry in the sample configuration files,
the translator cannot fully determine the type of key 
based on a single example value.
Consider the following example.

@@

>>>>

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. \app also allows users to 
provide extra help to the translator
for their specific system configurations,
but not necessarily. 
Each of the entries in the intermediate representations
have been assigned types, and these types guide the learning
modules later.

\para{Probabilistic types.}
For any key-value entry in the sample configuration files,
the translator cannot fully determine the type of key 
based on a single example value.
Consider the following example.

@@

\para{Formal Intermediate Representation.}
The formal grammar we use for our intermediate representation presented in the following. 
Firstly, we make a list of the possible types for a configuration file. This is present in 
Secondly, we

\begin{table}
  \begin{tabular}{| l | c | r |}
    \hline
    Type & Operation & 3 \\ \hline
    4 & 5 & 6 \\ \hline
    7 & 8 & 9 \\
    \hline
  \end{tabular}
\caption{Table of Types Along with Operation Pools}
\label{table:kysymys}
\end{table}

We come up with the following types:

1. Port 
The $i$-th entry inside an intermediate representation corresponding to a 
translated file

We declare a quadruple $(g,k,v,\{\tau_1, \ldots, \tau_n\}_i$
We need a kind of formal definition (using a figure) to
define the grammar of our intermediate representation. The basic
view of this definition should be similar to define a type language
grammar.
